---
title: "Aides Tests"
author: "Evelyn Corona"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
Atripla <- xtabs (~infected +group, data=Atriplavast) 
Atripla
```

         group
 infected drug placebo
     aids  103     131
     none 2163    2135

For group who was infected with AIDS, there were 103 who took Atriplavast, and 131 who took the placebo.

For group who was infected with None, there were 2136 who took Atriplavast, and 2135 who took the placebo.

Lets take a further look into the data. 

##Infected vs. Group Two-way table:

```{r}
rowPerc(Atripla)
```

         group
 infected   drug placebo  Total
   aids  44.02   55.98 100.00
   none  50.33   49.67 100.00
For the people who were infected with AIDS, 44.02% took Atriplavast, and 55.59% took the placebo.

For the people who were infected with None, 50.33% took Atriplavast and 49.67% took the placebo.

After reviewing the numerical data, people who were infected group with AIDS who took Atriplavast had a lower infection rate than those who took the placebo. The group who was not infected did not show much of a difference.

Lets look at the groups

##Group vs. Infected Two-way table:

```{r}
colPerc(Atripla)

```

        group
 infected   drug placebo
    aids    4.55    5.78
    none   95.45   94.22
  Total 100.00  100.00

For the people who took Atriplavast, 4.55% recieved AIDS, and 95.45% recieved none.

For the people who took the placebo, 5.78% recieved AIDS, and 94.22% recieved none.

After reviewing the numerical data, people who took Atriplavast who took Atriplavast had a lower AIDS infection rate than those who took the placebo. The group who was not infected did not show much of a difference.

Now that we have reviewed the numerical data, we will construct a bar chart to examine the graphical results of the data.

```{r}
barchartGC (Atripla, type="percent")
```


It appears that the people were infected with AIDS have a small difference in the ocuurence of it. The people who took Atriplavast recieved the virus less than those who took the placebo.

Now that we have graphically viewed that data, we will run an inferrential test to test their relationship

Let us begin by forming our two hypotheses:

\(H_0:\) Getting the AIDS virus is independent of taking Atriplavast.
\(H_A:\) Getting the AIDS virus is dependent of taking Atriplavast.

```{r}
chisqtestGC(Atripla)
```

 Pearson's Chi-squared test with Yates' continuity correction 
 
 Observed Counts:
         group
 infected drug placebo
     aids  103     131
     none 2163    2135
 
 Counts Expected by Null:
         group
 infected drug placebo
     aids  117     117
  none 2149    2149

  Contributions to the chi-square statistic:
         group
 infected drug placebo
   aids 1.68    1.68
     none 0.09    0.09
 
 
 Chi-Square Statistic = 3.285 
 Degrees of Freedom of the table = 1 
 P-Value = 0.0699

Our p-value from the ChiSquared test is approxoimatley 3.285, which suggests that, under a true null hypothesis, we have about a 3.285% probablity of returning a sample like this. The p-value must surpass the threshold of .05, in order to accept our null hypothesis as true. Since it does, we will accept the null hypothesis as true. Therefore, there is not a relationship between getting AIDS and taking Atriplavast.

Conclusion

From the three tests we ran on Atriplavast we have seen that there is not a relationship between the drug and the rate of infection. This does not show us that Atriplavast works well for treating AIDS.

Now we will look at the Atriplavast data for the Females

##Atriplavast Females

We will subset the data by sex to see if the drug is sex specific.

Let us review the numerical results

```{r}
AF<- filter(Atriplavast, sex=="F")
AF2<- xtabs (~infected +group, data=AF)
AF2
```

         group
 infected drug placebo
     aids   53      28
     none 1080    1105

For group of females who were infected with AIDS, there were 53 who took Atriplavast, and 28 who took the placebo.

For group of females who was infected with None, there were 1080 who took Atriplavast, and 1105 who took the placebo.

## Infected vs. Group Two-way table:

```{r}
rowPerc(AF2)
```

         group
 infected   drug placebo  Total
 aids  65.43   34.57 100.00
     none  49.43   50.57 100.00

For the females who were infected with AIDS, 65.43% took Atriplavast, and 34.57% took the placebo.

For the females who were infected with None, 49.43% took Atriplavast and 50.57% took the placebo.

After reviewing the numerical data, women in AIDS infected group, who took Atriplavast had a higher infection rate than those who took the placebo. The group who was not infected did not show much of a difference.

##Group vs. Infected Two-way table:

```{r}
colPerc(AF2)
```

         group
 infected   drug placebo
    aids    4.68    2.47
    none   95.32   97.53
    Total 100.00  100.00

For the females who took Atriplavast, 4.68% recieved AIDS, and 95.45% recieved none.

For the females who took the placebo, 2.47% recieved AIDS, and 97.53% recieved none.

After reviewing the numerical data, females who took Atriplavast had almost double the rate of AIDS infection rate than those who took the placebo. The group who was not infected reflected a small difference.

Now that we have reviewed the numerical data for women, we will construct a bar chart to examine the graphical results of the data.

```{r}
barchartGC (AF2, type="percent")
```


After inputing the data into a barchart, it appears that the female groups who were infected with AIDS have a large difference in the ocuurence. The females who took Atriplavast recieved the virus at a higher rate than those who took the placebo.

Now that we have graphically viewed that data, we will run an inferrential test to test their relationship

Let us begin by forming our two hypotheses:
\(H_0:\) For women, getting the AIDS virus is independent of taking Atriplavast.
\(H_A:\) For women, getting the AIDS virus is dependent of taking Atriplavast.

```{r}
chisqtestGC(AF2)
```

Pearson's Chi-squared test with Yates' continuity correction 
 
 Observed Counts:
         group
 infected drug placebo
     aids   53      28
 none 1080    1105
 
 Counts Expected by Null:
         group
 infected   drug placebo
     aids   40.5    40.5
     none 1092.5  1092.5
 
 Contributions to the chi-square statistic:
       group
 infected drug placebo
     aids 3.86    3.86
     none 0.14    0.14
 

 Chi-Square Statistic = 7.3747 
 Degrees of Freedom of the table = 1 
 P-Value = 0.0066

Our p-value from the ChiSquared test is approxoimatley 0.0066, which suggests that, under a true null hypothesis, we have about a 0.006% probablity of returning a sample like this. The p-value must surpass the threshold of .05, in order to accept our null hypothesis as true. Since it does not, we will reject the null hypothesis, therefore there is a relationship for females between getting AIDS and taking Atriplavast.

Conclusion

From the three tests we ran on the data from females, we have seen that there is a relationship between the drug and the rate of infection. We saw the differnces best in the barchart and the chi squared test. The barchart shows us that women who take Atriplavast had a higher occurrence of AIDS. From these tests we can conclude that, Women who take Atriplavast are more likely to get AIDS, and this does not show us that Atriplavast works well for treating AIDS in women.

Now for the men

##Atriplavast males
Let us review the numerical results

```{r}
AM<- filter (Atriplavast, sex=="M")
AM2<- xtabs (~infected +group, data=AM)
AM2
```

         group
 infected drug placebo
     aids   50     103
   none 1083    1030
For group of males who were infected with AIDS, there were 50 who took Atriplavast, and 103 who took the placebo.

For group of males who was infected with None, there were 1083 who took Atriplavast, and 1030 who took the placebo.

##Infected vs. Group Two-way table: 

```{r}

rowPerc(AM2)
```

         group
 infected   drug placebo  Total
     aids  32.68   67.32 100.00
     none  51.25   48.75 100.00
     
For the males who were infected with AIDS, 32.68% took Atriplavast, and 67.32% took the placebo.

For the males who were infected with None, 51.25% took Atriplavast and 48.75% took the placebo.

After reviewing the numerical data, the men in the AIDS infected group, who took Atriplavast had a much lower infection rate than those who took the placebo. The group who was not infected did show a small difference.

##Group vs. Infected Two-way table:

```{r}
colPerc(AM2)
```

         group
 infected   drug placebo
    aids    4.41    9.09
    none   95.59   90.91
    Total 100.00  100.00
    
For the males who took Atriplavast, 4.41% recieved AIDS, and 95.59% recieved none.

For the males who took the placebo, 9.09% recieved AIDS, and 90.91% recieved none.

After reviewing the numerical data, males who took Atriplavast had singificantly lower rate of AIDS infection rate, than those who took the placebo. The group who was not infected reflected a small difference.

Now that we have reviewed the numerical data for men, we will construct a bar chart to examine the graphical results of the data.

```{r}
barchartGC (AM2, type="percent")
```



After inputing the data for men into a barchart, it appears that the male groups who were infected with AIDS have a large difference in the ocuurence. The males who took Atriplavast recieved the virus at a lower rate than those who took the placebo.

Now that we have graphically viewed that data, we will run an inferrential test to test their relationship

Let us begin by forming our two hypotheses:
\(H_0:\) For men, getting the AIDS virus is independent of taking Atriplavast.
\(H_A:\) For men, getting the AIDS virus is dependent of taking Atriplavast.

```{r}
chisqtestGC(AM2)
```

 Pearson's Chi-squared test with Yates' continuity correction 

 Observed Counts:
         group
 infected drug placebo
     aids   50     103
     none 1083    1030
 
 Counts Expected by Null:
         group
 infected   drug placebo
     aids   76.5    76.5
     none 1056.5  1056.5
 
 Contributions to the chi-square statistic:
         group
 infected drug placebo
     aids 9.18    9.18
     none 0.66    0.66
 
 
 Chi-Square Statistic = 18.9529 
 Degrees of Freedom of the table = 1 
 P-Value = 0


Our p-value from the ChiSquared test is approxoimatley 0, which suggests that, under a true null hypothesis, we have about a 0% probablity of returning a sample like this. This is a significatly low value, and the p-value must surpass the threshold of .05, in order to accept our null hypothesis as true. Since it does not, we will reject the null hypothesis, therefore there is definetly a relationship for males between having AIDS and taking Atriplavast.

Conclusion

From the three tests we ran on the data from males, we have seen that there is a relationship between the Atriplavast and the rate of infenction, in men. We saw the relationship in all three tests. The numerical tests showed us the difference in infection rate between the treatment groups, this suggested men who took the drug were getting AIDS less. This was similar in the barchart where the relationship became visually apparent, the Atriplavast group with AIDS was much lower. And in the chi squared test, our p value suggested there is a relationship. From these tests we can conclude that there is a relationship for men between the AIDS virus and taking Atriplavast, men who take Atriplavast lower their porbability of not getting the AIDS virus.


# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






